---
title: "Developing Data Products - Week 4 Assignment"
author: "Dorothea L. Ugi"
date: "2/17/2020"
output: ioslides_presentation
---
## Reproducible Pitch

Peer assessed assignment for week 4 project of Coursera's Developing Data Products has two parts. First, create a Shiny application and deploy it on Rstudio's servers. Second, prepare a reproducible pitch presentation about your application.

Link: https://dugi/shinyapps.io/shiny/.

Code:

## Overview

The shiny app plots MPG vs different variables from the MTCARS dataset.

```{r }
head(mtcars)
```

## UI Code

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)
shinyUI(fluidPage(
  
  # Application title
  titlePanel("MTCARS Dataset - Miles per Gallon"),
  
  sidebarPanel(
    selectInput("variable", "Variable:", 
                c("Cylinders" = "cyl",
                  "Transmission" = "am",
                  "Carborators" = "carb",
                  "Gears" = "gear"))
    ),
  
  mainPanel(
    # Output: Formatted text for caption ----
    h3(textOutput("caption")),
    
    # Output: Plot of the requested variable vs mpg ----
    plotOutput("mpgPlot")
  )
))
```

## Server Code

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)
library(plotly)

inData <- mtcars
inData$am <- factor(inData$am, labels = c("Automatic", "Manual"))

shinyServer(function(input, output) {
  
  formulaText <- reactive({
    paste("MPG vs ", input$variable)
  })
  
  output$caption <- renderText({
    formulaText()
  })
  output$mpgPlot <- renderPlot({
    ggplot(inData, aes_string(y=input$variable, x="mpg")) + geom_point()
  })
  
})
```

